---
title: "P8105 Homework 5"
author: "Han Bao (hb2699)"
date: "2022-11-16"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(janitor)
library(readr)
library(rvest)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

### Problem 2

Import the dataset
```{r, message=FALSE}
data_url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide = read_csv(url(data_url)) 
```
The raw dataset collects data on homicides in 50 large U.S. cities. It has `r nrow(homicide)` observations of homicides and `r ncol(homicide)` key variables representing uid, reported date, victims' last name, first name, race, age, sex, city, state, latitude, longitude, and disposition.


Then we create a `city_state` variable and a `resolved` variable to indicate whether the homicides were solved. There was one observation was mis-recorded as "Tulsa, AL" and we plan to drop it since Tulsa is the city in the state of Oklahoma rather than Alabama.